Individual Differenes

### 2023-08-28 Analysis/e1_test.qmd
compare slope models

random_effects <- e1_vxBMM |> 
  gather_draws(`^r_id.*$`, regex = TRUE, ndraws = 1000) |> 
  separate(.variable, into = c("effect", "id", "term"), sep = "\\[|,|\\]") |> 
  mutate(id = factor(id,levels=levels(test$id))) |> 
  pivot_wider(names_from = term, values_from = .value) |> arrange(id,.chain,.draw,.iteration)

 indvDraws <- left_join(random_effects, fixed_effects, by = join_by(".chain", ".iteration", ".draw")) |> 
  rename(bandInt_RF = bandInt) |>
  right_join(new_data_grid, by = join_by("id")) |> 
  mutate(
    Slope = bandInt_RF+b_bandInt,
    estimate = (b_Intercept + Intercept) + (bandInt*(b_bandInt+bandInt_RF)) + (bandInt * condit_dummy) * `b_conditVaried:bandInt`
  )

  indvSlopes <- indvDraws |> group_by(id) |> median_qi(Slope)  |> 
  left_join(e1Sbjs, by=join_by(id)) |> group_by(condit) |>
  mutate(rankSlope=rank(Slope)) |> arrange(rankSlope)

  indvSlopes |> reframe(enframe(quantile(Slope, c(0.0,0.25, 0.5, 0.75,1)), "quantile", "Slope")) |> 
  pivot_wider(names_from=quantile,values_from=Slope,names_prefix="Q_") |>
  group_by(condit) |>
  summarise(across(starts_with("Q"), list(mean = mean))) |> kbl()

@@

```{r}
#| label: fig-e1-indv-slopes
#| fig-cap: Subset of Varied and Constant Participants with the largest estimated slope values. Red lines represent the best fitting line for each participant, gray lines are 200 random samples from the posterior distribution. Colored points and intervals at each band represent the empirical median and 95% HDI. 
#| fig-height: 11
nSbj <- 3
indvDraws  |> indv_model_plot(indv_coefs, testAvg, rank_variable=Estimate.bandInt,n_sbj=nSbj,"max")
indvDraws |> indv_model_plot(indv_coefs, testAvg, rank_variable=Estimate.bandInt,n_sbj=nSbj,"min")

>>>>

random_effects <- e1_vxBMM |> 
  gather_draws(`^r_id.*$`, regex = TRUE, ndraws = 1500) |> 
  separate(.variable, into = c("effect", "id", "term"), sep = "\\[|,|\\]") |> 
  mutate(id = factor(id,levels=levels(test$id))) |> 
  pivot_wider(names_from = term, values_from = .value) |> arrange(id,.chain,.draw,.iteration)

 indvDraws <- left_join(random_effects, fixed_effects, by = join_by(".chain", ".iteration", ".draw")) |> 
  rename(bandInt_RF = bandInt,RF_Intercept=Intercept) |>
  right_join(new_data_grid, by = join_by("id")) |> 
  mutate(
    Slope = bandInt_RF+b_bandInt,
    Intercept= RF_Intercept + b_Intercept,
    estimate = (b_Intercept + RF_Intercept) + (bandInt*(b_bandInt+bandInt_RF)) + (bandInt * condit_dummy) * `b_conditVaried:bandInt`,
  )

  indvSlopes <- indvDraws |> group_by(id) |> median_qi(Slope,SlopeInt,SlopeInt2, Intercept,b_Intercept,b_bandInt) |>
  left_join(e1Sbjs, by=join_by(id)) |> group_by(condit) |>
    select(id,condit,condit_dummy,Intercept,b_Intercept,Slope,SlopeInt,SlopeInt2,b_bandInt, n) |>
  mutate(rankSlope=rank(Slope)) |> arrange(rankSlope)   |> ungroup()

  indvSlopes |> group_by(condit) |> reframe(enframe(quantile(Slope, c(0.0,0.25, 0.5, 0.75,1)), "quantile", "Slope")) |> 
  pivot_wider(names_from=quantile,values_from=Slope,names_prefix="Q_") |>
  group_by(condit) |>
  summarise(across(starts_with("Q"), list(mean = mean))) |> kbl()

  indvSlopes |> reframe(enframe(quantile(SlopeInt, c(0.0,0.25, 0.5, 0.75,1)), "quantile", "SlopeInt")) |> 
  pivot_wider(names_from=quantile,values_from=SlopeInt,names_prefix="Q_") |>
  group_by(condit) |>
  summarise(across(starts_with("Q"), list(mean = mean))) |> kbl()

@@

```{r}
#| label: fig-e1-indv-slopes
#| fig-cap: Subset of Varied and Constant Participants with the smallest and largest estimated slope values. Red lines represent the best fitting line for each participant, gray lines are 200 random samples from the posterior distribution. Colored points and intervals at each band represent the empirical median and 95% HDI. 
#| fig-subcap: ["subset with largest slopes", "subset with smallest slopes"]
#| fig-height: 11
#| fig-width: 12
nSbj <- 3
indvDraws  |> indv_model_plot(indv_coefs, testAvg, Slope,rank_variable=Estimate.bandInt,n_sbj=nSbj,"max")
indvDraws |> indv_model_plot(indv_coefs, testAvg,Slope, rank_variable=Estimate.bandInt,n_sbj=nSbj,"min")

### 2023-08-28 Misc/indv_diff.qmd
compare slope models

---
title: Individual Differenes
date: last-modified
categories: [Analysis, R]
page-layout: full
toc: false
execute: 
  warning: false
  eval: false
---

```{r setup, include=FALSE}
source(here::here("Functions", "packages.R"))
test <- readRDS(here("data/e1_08-21-23.rds")) |> filter(expMode2 == "Test") 
options(brms.backend="cmdstanr",mc.cores=4)
e1Sbjs <- test |> group_by(id,condit) |> summarise(n=n())

testAvg <- test %>% group_by(id, condit, vb, bandInt,bandType,tOrder) %>%
  summarise(nHits=sum(dist==0),vx=mean(vx),dist=mean(dist),sdist=mean(sdist),n=n(),Percent_Hit=nHits/n)

@@

combined_df <- left_join(random_effects, fixed_effects, by = join_by(".chain", ".iteration", ".draw")) |> 
  rename(bandInt_RF = bandInt) |>
  right_join(new_data_grid, by = join_by("id")) |> 
  mutate(
    fixed_effects = b_Intercept +
      (bandInt * b_bandInt) +
      condit_dummy * b_conditVaried + 
      (bandInt * condit_dummy) * `b_conditVaried:bandInt` ,  
    random_effects = Intercept + bandInt_RF,  # Assuming random effects for intercept and bandInt
    estimate = (b_Intercept + Intercept) + (bandInt*(b_bandInt+bandInt_RF)) + (bandInt * condit_dummy) * `b_conditVaried:bandInt`
  )

@@

@@

indv_model_plot <- function(combined_df, indv_coefs, testAvg, rank_variable = "Estimate.Intercept", n_sbj = 5, order = "min") {
  slice_fn <- if (order == "min") slice_min else slice_max
  combined_df  |> 
    filter(id %in% (indv_coefs  |> 
                      slice_fn({{ rank_variable }}, n = n_sbj, by = condit) |> 
                      pull(id)))  |> 
    group_by(id, bandInt)  |> 
    sample_n(50)  |> 
    ggplot(aes(x = bandInt, y = estimate)) +
    geom_abline(aes(intercept = Intercept + b_Intercept, slope = bandInt_RF + b_bandInt), color = "grey50") +
    geom_abline(data = indv_coefs  |> 
                  slice_fn({{ rank_variable }}, n = n_sbj, by = condit),
                aes(intercept = Estimate.Intercept, slope = Estimate.bandInt), color = "red") +
    stat_halfeye() +
    stat_halfeye(data = testAvg  |> 
                   filter(id %in% (indv_coefs |> slice_fn({{ rank_variable }}, n = n_sbj, by = condit) |> 
                      pull(id))), 
                 aes(x = bandInt, y = vx), color = "blue") +
    ggh4x::facet_nested_wrap(vars(condit, id),ncol=3)
}

@@

```{r fig.width=12, fig.height=11}

coef(e1_vxBMM)$id %>% as_tibble(rownames="id") %>% select(id, starts_with("Est")) |> print(n=15)

@@

df_pred <- 
  posterior_predict(e1_distBMM, ndraws = 500) |>
  array_branch(margin=1) |> 
   map_dfr( 
    function(yrep_iter) {
      test %>%
        mutate(dist_pred = yrep_iter)
    },
    .id = 'iter'
  ) |>
  mutate(iter = as.numeric(iter))

@@

vx_pred <- 
  posterior_predict(e1_vxBMM, ndraws = 500) |> 
  array_branch(margin=1) |> 
   map_dfr( 
    function(yrep_iter) {
      test %>%
        mutate(vx_pred = yrep_iter)
    },
    .id = 'iter'
  ) %>%
  mutate(iter = as.numeric(iter))

@@

df_posterior <- e1_vxBMM |> as_tibble()

>>>>

---
title: Individual Differenes
date: last-modified
categories: [Analysis, R]
page-layout: full
toc: false
execute: 
  warning: false
  eval: true
---

```{r setup, include=FALSE}
source(here::here("Functions", "packages.R"))
test <- readRDS(here("data/e1_08-21-23.rds")) |> filter(expMode2 == "Test") 
options(brms.backend="cmdstanr",mc.cores=4)
e1Sbjs <- test |> group_by(id,condit) |> summarise(n=n()) |>
  mutate(condit_dummy = ifelse(condit == "Varied", 1, 0))

testAvg <- test %>% group_by(id, condit, vb, bandInt,bandType,tOrder) %>%
  summarise(nHits=sum(dist==0),vx=mean(vx),dist=mean(dist),sdist=mean(sdist),n=n(),Percent_Hit=nHits/n) |> ungroup()

@@

 indvDraws <- left_join(random_effects, fixed_effects, by = join_by(".chain", ".iteration", ".draw")) |> 
  rename(bandInt_RF = bandInt,RF_Intercept=Intercept) |>
  right_join(new_data_grid, by = join_by("id")) |> 
  mutate(
    Slope = bandInt_RF+b_bandInt,
    Intercept= RF_Intercept + b_Intercept,
    estimate = (b_Intercept + RF_Intercept) + (bandInt*(b_bandInt+bandInt_RF)) + (bandInt * condit_dummy) * `b_conditVaried:bandInt`,
    SlopeInt=bandInt_RF+b_bandInt + ((`b_conditVaried:bandInt` + bandInt_RF)*condit_dummy),
    SlopeInt2=bandInt_RF+b_bandInt + ((`b_conditVaried:bandInt` + b_bandInt)*condit_dummy)
  )

  indvSlopes <- indvDraws |> group_by(id) |> median_qi(Slope,SlopeInt,SlopeInt2, Intercept,b_Intercept,b_bandInt) |>
  left_join(e1Sbjs, by=join_by(id)) |> group_by(condit) |>
    select(id,condit,condit_dummy,Intercept,b_Intercept,Slope,SlopeInt,SlopeInt2,b_bandInt, n) |>
  mutate(rankSlope=rank(Slope)) |> arrange(rankSlope)   |> ungroup()

@@

full_tab <- testAvg |> select(id,condit,vx,vb,bandInt) |> 
  left_join(indvDraws |> group_by(id,bandInt) |> median_qi(estimate,Intercept,Slope), by=join_by(id,bandInt)) |>
  mutate(resid=vx-estimate) |> relocate(vx,resid,.before=estimate) |>
  mutate(across(where(is.numeric), \(x) round(x,0)))

full_tab |> group_by(condit) |> summarise(mean(resid),sd(resid))
full_tab |> group_by(condit,id) |> summarise(m=mean(resid),s=sd(resid)) |> summarise(m=mean(m),s=sd(s))

full_tab |> DT::datatable(options = list(pageLength=15))
```

```{r}
  indvSlopes |> group_by(condit) |> reframe(enframe(quantile(Slope, c(0.0,0.25, 0.5, 0.75,1)), "quantile", "Slope")) |> 
  pivot_wider(names_from=quantile,values_from=Slope,names_prefix="Q_") |>
  group_by(condit) |>
  summarise(across(starts_with("Q"), list(mean = mean))) |> kbl()

  indvSlopes |> group_by(condit)  |> reframe(enframe(quantile(SlopeInt, c(0.0,0.25, 0.5, 0.75,1)), "quantile", "SlopeInt")) |> 
  pivot_wider(names_from=quantile,values_from=SlopeInt,names_prefix="Q_") |>
  group_by(condit) |>
  summarise(across(starts_with("Q"), list(mean = mean))) |> kbl()

  indvSlopes |> group_by(condit)  |> reframe(enframe(quantile(SlopeInt2, c(0.0,0.25, 0.5, 0.75,1)), "quantile", "SlopeInt2")) |> 
  pivot_wider(names_from=quantile,values_from=SlopeInt2,names_prefix="Q_") |>
  group_by(condit) |>
  summarise(across(starts_with("Q"), list(mean = mean))) |> kbl()

  ggplot(indvSlopes, aes(x = Slope, color = condit)) + 
  geom_density() 
    ggplot(indvSlopes, aes(x = SlopeInt, color = condit)) + 
  geom_density() 
```

```{r fig.width=13, fig.height=12.5}

  n_sbj = 3

{indvDraws |> filter(condit=="Varied")  |> 
   indv_model_plot(indvSlopes |> filter(condit=="Varied"), 
                   testAvg |> filter(condit=="Varied"),slopeVar=Slope, rank_variable=Slope,n_sbj=n_sbj,"max") + 
     ggtitle("Slope = bandInt_RF+b_bandInt") } /

{indvDraws |> filter(condit=="Varied")  |> 
  indv_model_plot(indvSlopes |> filter(condit=="Varied"), 
                  testAvg |> filter(condit=="Varied"),slopeVar=SlopeInt, rank_variable=Slope,n_sbj=n_sbj,"max")  + 
     ggtitle("SlopeInt=bandInt_RF+b_bandInt + ((`b_conditVaried:bandInt` + bandInt_RF)*condit_dummy)") } /

indvDraws |> filter(condit=="Varied")  |> 
  indv_model_plot(indvSlopes |> filter(condit=="Varied"), 
                  testAvg |> filter(condit=="Varied"),slopeVar=SlopeInt2, rank_variable=Slope,n_sbj=n_sbj,"max") + 
     ggtitle("SlopeInt2=bandInt_RF+b_bandInt + ((`b_conditVaried:bandInt` + b_bandInt)*condit_dummy)")

{indvDraws |> filter(condit=="Varied")  |> 
   indv_model_plot(indvSlopes |> filter(condit=="Varied"), 
                   test |> filter(condit=="Varied"),slopeVar=Slope, rank_variable=Slope,n_sbj=n_sbj,"max") + 
     ggtitle("Slope = bandInt_RF+b_bandInt") } /

{indvDraws |> filter(condit=="Varied")  |> 
  indv_model_plot(indvSlopes |> filter(condit=="Varied"), 
                  test |> filter(condit=="Varied"),slopeVar=SlopeInt, rank_variable=Slope,n_sbj=n_sbj,"max")  + 
     ggtitle("SlopeInt=bandInt_RF+b_bandInt + ((`b_conditVaried:bandInt` + bandInt_RF)*condit_dummy)") } /

indvDraws |> filter(condit=="Varied")  |> 
  indv_model_plot(indvSlopes |> filter(condit=="Varied"), 
                  test |> filter(condit=="Varied"),slopeVar=SlopeInt2, rank_variable=Slope,n_sbj=n_sbj,"max") + 
     ggtitle("SlopeInt2=bandInt_RF+b_bandInt + ((`b_conditVaried:bandInt` + b_bandInt)*condit_dummy)")

```{r fig.height=15, fig.width=12}
#| fig-height: 16
#| fig-width: 12
{indvDraws  |> indv_model_plot(indvSlopes, test,slopeVar=Slope, rank_variable=Slope,n_sbj=n_sbj,"max") + 
     ggtitle("Slope = bandInt_RF+b_bandInt") } /
 {ggplot(indvSlopes, aes(x = Slope, color = condit)) + geom_density() } /
#gridExtra::tableGrob( indvSlopes |> group_by(condit) |> summarise(Mean=mean(Slope),Sd=sd(Slope)) ) + 
  gt_temp(indvSlopes |> group_by(condit) |> summarise(Mean=mean(Slope),Sd=sd(Slope)) ) +
  plot_layout(heights=unit(c(16,6,3),c('cm'))) + plot_annotation("vx ~ condit * bandInt + (1 + bandInt | id) ")
```

Band Only Model
```{r fig.width=11, fig.height=15}
#| fig-height: 16
#| fig-width: 12
e1_testVx_grRF8 <- readRDS(here::here("data/model_cache/e1_testVx_grRF8.rds"))
# e1_testVx_grRF8$formula
# vx ~ bandInt + (1 + bandInt || gr(id, by = condit))

new_data_grid=map_dfr(1, ~data.frame(unique(test[,c("id","bandInt")]))) |> 
  dplyr::arrange(id,bandInt)

fixed_effects <- e1_testVx_grRF8 |> 
  spread_draws(`^b_.*`,regex=TRUE) |> arrange(.chain,.draw,.iteration)

random_effects <- e1_testVx_grRF8 |> 
  gather_draws(`^r_id.*$`, regex = TRUE, ndraws = 1000) |> 
  separate(.variable, into = c("effect", "id", "term"), sep = "\\[|,|\\]") |> 
  mutate(id = factor(id,levels=levels(test$id))) |> 
  pivot_wider(names_from = term, values_from = .value) |> arrange(id,.chain,.draw,.iteration)

indvDraws <- left_join(random_effects, fixed_effects, by = join_by(".chain", ".iteration", ".draw")) |> 
  rename(bandInt_RF = bandInt,RF_Intercept=Intercept) %>%
  right_join(e1Sbjs,., by=join_by(id)) |>
  right_join(new_data_grid, by = join_by("id")) |> 
  mutate(
    Slope = bandInt_RF+b_bandInt,
    Intercept= RF_Intercept + b_Intercept,
    estimate = (b_Intercept + RF_Intercept) + (bandInt*(b_bandInt+bandInt_RF)),
  )

indvSlopes <- indvDraws |> group_by(id) |> median_qi(RF_Intercept,b_Intercept,Intercept,bandInt_RF,b_bandInt,Slope) |>
  left_join(e1Sbjs, by=join_by(id)) |> group_by(condit) |>
    select(id,condit,RF_Intercept,b_Intercept,Intercept,bandInt_RF,b_bandInt,Slope, n) |>
  ungroup() |>
  mutate(rankSlope=rank(Slope), 
         Slope2 = ((coef(e1_testVx_grRF8)$id |> as_tibble(rownames="id") ) |> pull(Estimate.bandInt)) )

{ indvDraws |> indv_model_plot(indvSlopes ,test, slopeVar=Slope, rank_variable=Slope,n_sbj=n_sbj,"max") + 
     ggtitle("Slope = bandInt_RF+b_bandInt") } /
 {ggplot(indvSlopes, aes(x = Slope, color = condit)) + geom_density() } /
#gridExtra::tableGrob( indvSlopes |> group_by(condit) |> summarise(Mean=mean(Slope),Sd=sd(Slope)) ) + 
  gt_temp(indvSlopes |> group_by(condit) |> summarise(Mean=mean(Slope),Sd=sd(Slope)) ) +
  plot_layout(heights=unit(c(16,6,2),c('cm'))) + plot_annotation("vx ~ bandInt + (1 + bandInt || gr(id, by = condit))  ")

```{r}
noInt_tab <- testAvg |> select(id,condit,vx,vb,bandInt) |> 
  left_join(indvDraws |> group_by(id,bandInt) |> median_qi(estimate,Intercept,Slope), by=join_by(id,bandInt)) |>
  mutate(resid=vx-estimate) |> relocate(vx,resid,.before=estimate) |>
  mutate(across(where(is.numeric), \(x) round(x,0)))

noInt_tab |> group_by(condit) |> summarise(mean(resid),sd(resid))
noInt_tab |> group_by(condit,id) |> summarise(m=mean(resid),s=sd(resid)) |> summarise(m=mean(m),s=sd(s))

noInt_tab |> DT::datatable(options = list(pageLength=15))
```

```{r fig.height=9,fig.width=10}
#| eval: false
random_effects |> group_by(id) |> median_hdi()

indv_coefs |> select(id,condit,Estimate.bandInt)
indv_coefs |> select(id,condit,Estimate.bandInt) |> group_by(condit) |> summarise(mean(Estimate.bandInt))

fixef(e1_vxBMM)
ranef(e1_vxBMM)$id[, ,"bandInt"] |> as_tibble(rownames="id") |> 
  left_join(e1Sbjs,by=join_by(id)) |>
  group_by(condit) |> summarise(mean(Estimate))

ranef(e1_vxBMM)$id[, ,"bandInt"] |> as_tibble(rownames="id") |> 
  left_join(e1Sbjs,by=join_by(id)) |> ggplot(aes(Estimate,color=condit)) + geom_density()

popSlope <- tidy(e1_vxBMM, effects = "fixed") |> filter(term=="bandInt") |> pull(estimate)
popInteraction <- tidy(e1_vxBMM, effects = "fixed") |> filter(term=="conditVaried:bandInt") |> pull(estimate)

e1Vx <- ranef(e1_vxBMM)$id[, ,"bandInt"] |> as_tibble(rownames="id") %>%
  left_join(e1Sbjs,., by=join_by(id)) |> select(id,condit,condit_dummy,Estimate) |> 
  mutate(pop=popSlope,Slope1=Estimate + pop) |> 
  left_join(indv_coefs |> select(id,Slope2=Estimate.bandInt), join_by(id)) |>
  mutate(Slope3=Estimate + pop + ((popInteraction + Estimate)*condit_dummy))

e1Vx |> group_by(condit) |> summarise(Slope_with_int=mean(Slope3), sd_Slope=sd(Slope3))

e1Vx |> group_by(condit) |> reframe(enframe(quantile(Slope3, c(0.0,0.25, 0.5, 0.75,1)), "quantile", "Slope3")) |> 
  pivot_wider(names_from=quantile,values_from=Slope3,names_prefix="Q_") |>
  group_by(condit) |>
  summarise(across(starts_with("Q"), list(mean = mean))) |> kbl()

{ e1Vx |> ggplot(aes(Slope1,color=condit)) + geom_density() +ggtitle("RF_Estimate + Population_Est") } /
e1Vx |> ggplot(aes(Slope3,color=condit)) + geom_density() + 
  ggtitle("Slope3=Estimate + pop + ((popInteraction + Estimate)*condit_dummy)")

Examine slopes from different models

```{r fig.height=10,fig.width=9}
#| eval: false 
#| 
# vx ~ bandInt + (1 + bandInt || gr(id, by = condit)) 
bandOnly <- ranef(e1_testVx_grRF8)$id[, ,"bandInt"] |> as_tibble(rownames="id") |> 
  left_join(e1Sbjs,by=join_by(id)) |> select(id,condit,condit_dummy,starts_with("Estimate")) |>
 # group_by(condit) |> 
  #summarise(Estimate=mean(Estimate)) |>
  mutate(pop = tidy(e1_testVx_grRF8, effects = "fixed") |> filter(term=="bandInt") |> pull(estimate),
         Slope1=pop+Estimate,
         Slope2 = (coef(e1_testVx_grRF8)$id |> as_tibble(rownames="id") |> pull(Estimate.bandInt)))

# vx ~ condit + bandInt + (1 + bandInt | id) 
noInt <- ranef(e1_conditPlusBand_RF)$id[, ,"bandInt"] |> as_tibble(rownames="id") |> 
  left_join(e1Sbjs,by=join_by(id)) |> select(id,condit,condit_dummy,starts_with("Estimate")) |>
 # group_by(condit) |> 
  #summarise(Estimate=mean(Estimate)) |>
  mutate(pop = tidy(e1_conditPlusBand_RF, effects = "fixed") |> filter(term=="bandInt") |> pull(estimate),
         Slope1=pop+Estimate,
         Slope2 = (coef(e1_conditPlusBand_RF)$id |> as_tibble(rownames="id") |> pull(Estimate.bandInt)))

# vx ~ condit * bandInt + (1 + bandInt | gr(id, by = condit)) 
popSlope <- tidy(e1_testVxBand_grRF, effects = "fixed") |> filter(term=="bandInt") |> pull(estimate)
popInteraction <- tidy(e1_testVxBand_grRF, effects = "fixed") |> filter(term=="conditVaried:bandInt") |> pull(estimate)
vx_grRF <- ranef(e1_testVxBand_grRF)$id[, ,"bandInt"] |> as_tibble(rownames="id") |> 
  left_join(e1Sbjs,by=join_by(id)) |> select(id,condit,condit_dummy,starts_with("Estimate")) |>
 # group_by(condit) |> 
  #summarise(Estimate=mean(Estimate)) |>
  mutate(pop = tidy(e1_testVxBand_grRF, effects = "fixed") |> filter(term=="bandInt") |> pull(estimate),
         Slope1=pop+Estimate,
         Slope2 = (coef(e1_testVxBand_grRF)$id |> as_tibble(rownames="id") |> pull(Estimate.bandInt)), 
         Slope3=Estimate + pop + ((popInteraction + Estimate)*condit_dummy))

bandOnly |> group_by(condit) |> summarise(Estimate=mean(Slope1))
noInt |> group_by(condit) |> summarise(Estimate=mean(Slope1))
vx_grRF |> group_by(condit) |> summarise(Estimate=mean(Slope3))

modelsummary(list("Band Only" = e1_testVx_grRF8,
                  "No Interaction" = e1_conditPlusBand_RF,
                  "Full Model - Gr" = e1_testVxBand_grRF,
                  "Full Model" = e1_vxBMM),
             coef_map = c("b_Intercept"="Intercept","b_bandInt"="Band Slope", "b_conditVaried"="Condition",
                          'b_conditVaried:bandInt'="Interaction","sigma"="Sigma"),
             output="markdown",gof_map=NA,fmt=2)

{ bandOnly |> ggplot(aes(Slope1,color=condit)) + geom_density() + 
  ggtitle("vx ~ bandInt + (1 + bandInt || gr(id, by = condit))") } /
  { noInt |> ggplot(aes(Slope1,color=condit)) + geom_density() + 
  ggtitle("vx ~ condit + bandInt + (1 + bandInt | id)  ") } / 
{ vx_grRF |> ggplot(aes(Slope3,color=condit)) + geom_density() + 
  ggtitle("vx ~ condit * bandInt + (1 + bandInt | gr(id, by = condit)) ") } /
{ e1Vx |> ggplot(aes(Slope3,color=condit)) + geom_density() + 
  ggtitle("vx ~ condit * bandInt + (1 + bandInt | id) ") }

bandOnly |> group_by(condit) |> reframe(enframe(quantile(Slope1, c(0.0,0.25, 0.5, 0.75,1)), "quantile", "Slope1")) |> 
  pivot_wider(names_from=quantile,values_from=Slope1,names_prefix="Q_") |>
  group_by(condit) |>
  summarise(across(starts_with("Q"), list(mean = mean))) |> 
  pandoc.table(caption="vx ~ bandInt + (1 + bandInt || gr(id, by = condit))")

noInt |> group_by(condit) |> reframe(enframe(quantile(Slope1, c(0.0,0.25, 0.5, 0.75,1)), "quantile", "Slope1")) |> 
  pivot_wider(names_from=quantile,values_from=Slope1,names_prefix="Q_") |>
  group_by(condit) |>
  summarise(across(starts_with("Q"), list(mean = mean))) |> 
  pandoc.table(caption="vx ~ condit + bandInt + (1 + bandInt | id)  ")

vx_grRF |> group_by(condit) |> reframe(enframe(quantile(Slope3, c(0.0,0.25, 0.5, 0.75,1)), "quantile", "Slope1")) |> 
  pivot_wider(names_from=quantile,values_from=Slope1,names_prefix="Q_") |>
  group_by(condit) |>
  summarise(across(starts_with("Q"), list(mean = mean))) |> 
  pandoc.table(caption="vx ~ condit * bandInt + (1 + bandInt | gr(id, by = condit))  ")

e1Vx |> group_by(condit) |> reframe(enframe(quantile(Slope3, c(0.0,0.25, 0.5, 0.75,1)), "quantile", "Slope3")) |> 
  pivot_wider(names_from=quantile,values_from=Slope3,names_prefix="Q_") |>
  group_by(condit) |>
  summarise(across(starts_with("Q"), list(mean = mean))) |>
  pandoc.table(caption="vx ~ condit * bandInt + (1 + bandInt | id)  ")

@@

@@

```{r fig.width=12, fig.height=11}
#| eval: false
coef(e1_vxBMM)$id %>% as_tibble(rownames="id") %>% select(id, starts_with("Est")) |> print(n=15)

@@

```{r}
#| eval: false
df_pred <- 
  posterior_predict(e1_distBMM, ndraws = 500) |>
  array_branch(margin=1) |> 
   map_dfr( 
    function(yrep_iter) {
      test %>%
        mutate(dist_pred = yrep_iter)
    },
    .id = 'iter'
  ) |>
  mutate(iter = as.numeric(iter))

@@

```{r}
#| eval: false
vx_pred <- 
  posterior_predict(e1_vxBMM, ndraws = 500) |> 
  array_branch(margin=1) |> 
   map_dfr( 
    function(yrep_iter) {
      test %>%
        mutate(vx_pred = yrep_iter)
    },
    .id = 'iter'
  ) %>%
  mutate(iter = as.numeric(iter))

@@

```{r}
#| eval: false
df_posterior <- e1_vxBMM |> as_tibble()
